---
output: github_document
bibliography: bib.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Reproduce the Results of @gerard2020fast

## Introduction

This repository contains the code and instructions needed to reproduce all of
the results from @gerard2020fast.

## Instructions

You will need an up-to-date version of R, GNU make, and 7zip. To install the required R packages, run the following in R:
```{r, eval = FALSE}
install.packages(c("updog", 
                   "ldsep", 
                   "tidyverse", 
                   "vcfR",
                   "foreach",
                   "doParallel", 
                   "ggthemes", 
                   "latex2exp"))
```

To run all simulations, open up the terminal and run

```{bash, eval = FALSE}
make
```

# Additional Results

Mathematica code for calculating the gradients necessary for standard error calculations can be found at [here](./code/gradients.nb) and [here](./code/gradients.md).

A description of the simulation figures in "./output/sims" can be found [here](./output/sims/README.md).

# Session Information

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
lapply(c("updog", 
         "ldsep", 
         "tidyverse", 
         "vcfR",
         "foreach",
         "doParallel", 
         "ggthemes", 
         "latex2exp"), 
       FUN = library,
       character.only = TRUE)
```
```{r, echo = FALSE}
sessionInfo()
```


## References
