---
output: github_document
bibliography: bib.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Reproduce the Results of @gerard2021fast

[![DOI](https://zenodo.org/badge/289036114.svg)](https://zenodo.org/badge/latestdoi/289036114)

## Introduction

This repository contains the code and instructions needed to reproduce all of
the results from @gerard2021fast.

## Instructions

- You will need an up-to-date version of R, GNU make, and 7zip. To install the required R packages, run the following in R:

    ```{r, eval = FALSE}
    install.packages(c("updog", 
                       "devtools", 
                       "tidyverse", 
                       "vcfR",
                       "foreach",
                       "doParallel", 
                       "ggthemes", 
                       "GGally",
                       "gridExtra",
                       "latex2exp",
                       "matrixStats",
                       "ashr",
                       "ldsep"))
    ```

- To run all analyses, open up the terminal and run

    ```{bash, eval = FALSE}
    make
    ```

- To run just the simulations, run

    ```{bash, eval = FALSE}
    make sims
    ```

- To run just the real data analyses using the data from 
@uitdewilligen2013next, run

    ```{bash, eval = FALSE}
    make uit
    ```

- Note that running these scripts will result in downloading the real datasets
used. But you can also download them directly from:

    - <https://doi.org/10.1371/journal.pone.0062355.s004>
    - <https://doi.org/10.1371/journal.pone.0062355.s007>
    - <https://doi.org/10.1371/journal.pone.0062355.s009>
    - <https://doi.org/10.1371/journal.pone.0062355.s010>

    Just make sure that you then place them in the "./data/uit/" directory.

# Additional Results

Mathematica code for calculating the gradients necessary for standard error calculations can be found at [here](./code/gradients.nb) and [here](./code/gradients.md).

A description of the simulation figures in "./output/sims" can be found [here](./output/sims/README.md).

# Session Information

```{r, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
lapply(c("updog", 
         "ldsep", 
         "devtools",
         "tidyverse", 
         "vcfR",
         "foreach",
         "doParallel", 
         "ggthemes", 
         "GGally",
         "gridExtra",
         "latex2exp",
         "matrixStats",
         "ashr"), 
       FUN = library,
       character.only = TRUE)
```
```{r, echo = FALSE}
sessionInfo()
```

## References
